Title here

### 2016-09-27 portfolio/text/ms.Rmd
Reorder figures and results

- What's novel
    - Huge dataset
    - Permit level data (on individuals, not vessels)
    - Account for covariates
    - Accounting for strategies
    - Keeping annual data (not condensing to mean and cv)
    - Joint modelling of mean and variance
    - look at different mechanisms of diversification
- Suggests it's mostly an across strategy/permit effect (lowering variability),
  which isn't always a possibility because of regulations and cost
- Adjusting within current permit constraints is risky... Not clearly risk
  reducing to generalize from one year to the next
- not as simple as increase diversity (within permit) and reduce risk
- 2 dimensions to think about (revenue and variability); and the trade-off is fishery specific
    - effects within a permit strategy are permit specific
    - Importantly it's a tradeoff - 2 dimensions - sometimes make more money by specializing... Some highly variable single species permits make a ton of money... which preferable?

>>>>

- Suggests it's mostly an across strategy/permit effect (lowering variability),
  which isn't always a possibility because of regulations and cost
- Adjusting within current permit constraints is risky... Not clearly risk
  reducing to generalize from one year to the next
- not as simple as increase diversity (within permit) and reduce risk
- What's methodologically novel
    - Huge dataset
    - Permit level data (on individuals, not vessels)
    - Account for covariates
    - Accounting for strategies
    - Keeping annual data (not condensing to mean and cv)
    - Joint modelling of mean and variance
    - look at different mechanisms of diversification
- 2 dimensions to think about (revenue and variability); and the trade-off is fishery specific
    - effects within a permit strategy are permit specific
    - Importantly it's a tradeoff - 2 dimensions - sometimes make more money by specializing... Some highly variable single species permits make a ton of money... which preferable?
